Output Summary

### 2023-03-31 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Discard Yr0 resids from MCMC diagnostics
Must be forced to zero in this parameterization unfortunately

JAGS returns "cannot find appropriate sample for Tau" if you try to invert it, insert the sig_init parameter, then reinvert for usage to inform the yr0 resid. I've had to do this before, and am not concerned with it affecting any model inference

# parr recruitment
L1 = "Egg-to-Parr Survival"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "White Noise Process SD", "AR(1) Coefficient", "Initial Residual", "Among-pop Correlation", "Realized")
match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "kappa_phi_E_Pb", "Lphi_E_Pb_resid[1,", "rho_Lphi_E_Pb", "^phi_E_Pb[")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("Yr1 NOR:HOR Scaler", "Yr2 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
base = c("delta_O0_O1[pop]", "delta_O1_O2[pop]", "Lphi_O0_O1_resid[1,1,pop]", "kappa_phi_O0_O1[pop]")
match = sub_index(base, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

>>>>

# parr recruitment
L1 = "Egg-to-Parr Survival"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "White Noise Process SD", "AR(1) Coefficient", "Among-pop Correlation", "Realized")
match = c("alpha", "^beta[", "^lambda$", "sig_lbeta", "sig_Lphi_E_Pb", "kappa_phi_E_Pb", "rho_Lphi_E_Pb", "^phi_E_Pb[")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

@@

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("Yr1 NOR:HOR Scaler", "Yr 1 AR(1) Coefficient")
base = c("delta_O0_O1[pop]", "kappa_phi_O0_O1[pop]")
match = sub_index(base, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
